A Large-Area, Spatially Continuous Assessment of Land Cover Map Error and Its Impact on Downstream Analyses

### 2017-04-25 paper/main.tex
Revert back to auth-date citation for GCB

\documentclass[a4paper]{article}
\usepackage[affil-it]{authblk}    
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
%\usepackage{endfloat}
\usepackage{float}
\usepackage[sort,compress]{natbib}
%\bibpunct{[}{]}{,}{n}{,}{,}  % https://xianblog.wordpress.com/tag/natbib/ (allows natbib with PNAS)
\usepackage{endnotes}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[left=2.5cm, right=2.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
%\usepackage{mathtime}
\usepackage{bm}
\usepackage{url}
%\usepackage{babel}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{boldline}
\setcellgapes{3pt}
\usepackage[flushleft]{threeparttable}
\usepackage{wrapfig}
\newcommand{\citetapos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
%%%%%

@@

\begin{figure*}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\centerline{\includegraphics[width=1\textwidth]{figures/figure1.pdf}}
\vspace{-0.15 cm}
\caption{(A) Errors in the percent cropland estimates resulting from each of the four test maps relative to the reference map at different scale of pixel aggregation. Rows indicate the test map being assessed (by subtraction from the reference map), while columns refer to resolution of aggregation. White indicates areas where areas under communal farmlands or permanent tree crops were removed from analysis. (B) The bias (mean error) and accuracy (mean absolute error [MAE]) of each test map at each scale of aggregation, weighted by the percentage cropland in each cell of the reference map. Bias estimates are indicated by the semi-transparent bars, accuracy (lower is more accurate) by the solid bars, with bar colors coded to specific cropland maps.}
\label{afoto1}
\end{figure*}

@@

%\vspace{-0.75 cm}
%\begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[!h]
%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/biases_md_lnorm_gam_mu0.pdf}}
\centerline{\includegraphics[width=.7\textwidth]{figures/biases_md_lnorm_gam_mu0.pdf}}
\caption{The relationship between map accuracy (the mean absolute error) in test maps and the actual cropland cover within agricultural landscapes (reference map pixels having $>$0.5\% cropland), here defined by the boundaries of magisterial districts (n = 345), as fit with a generalized additive model. Prediction curves are color-coded to the different test maps, with the solid line indicating predicted absolute bias, and the lighter shading the standard error of the coefficients.}\label{afoto2}
\end{figure}
%\end{wrapfigure}
%\vspace{-0.75 cm}

@@

%\vspace{-0.75 cm}
\begin{figure}[!h]
%\begin{wrapfigure}{r}{0.5\textwidth}
%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/figure3.pdf}}
\centerline{\includegraphics[width=0.55\textwidth]{figures/figure3.pdf}}
\caption{Biases and accuracies (mean absolute errors) of carbon densities derived from cropland maps, calculated as percents relative to the reference map. Bias estimates (represented by symbols) fall within the semi-transparent floating bars, while accuracies are contained in the solid bars. Bar colors are coded to specific cropland map, symbols indicate which cover type was used to calculate cropland-adjacent carbon density. The bar represents the mean biases calculated across each of the 5 cover types. Shrubland and grassland bias values were near zero, while secondary forest values were close to forest values, and thus these are not shown for display clarity (but see Table S2). MODIS and GlobCover values at 1 km exceeding the plot's Y limits are provided near their truncated tops.}
\label{afoto}
\end{figure}
%\end{wrapfigure}

@@

SA-LC and GeoWiki also resulted in ET errors estimates along the southern and western coasts, but here the tendency was to underestimate ET, while biases in the center of the country were either negligible to absent.  All but MODIS underestimated ET by 5-15\% in the northern tip of the country.

%\vspace{-0.75 cm}
\begin{figure}[h]
\centerline{\includegraphics[width=.6\textwidth]{figures/et_bias_map.pdf}}
\caption{Differences in annual mean evapotranspiration estimates from 29-year runs of the VIC land surface hydrology model when initialized with LAI response curves derived from the reference map, versus those from the four test maps.}\label{afoto}
\end{figure}

@@

%\vspace{-0.5 cm}
\begin{figure}[!ht]
%\vspace{-0.75 cm}
\centerline{\includegraphics[width=0.55\textwidth]{figures/yield_prod_bias.pdf}}
\caption{Bias (mean error) and accuracy (mean absolute error [MAE]) in disaggregated maize yield and production estimates. Bias estimates (represented by symbols) fall within the semi-transparent bars, mean absolute errors in the solid bars, with bar colors coded to specific cropland maps.  Symbols code the different variables (production and yield), normalized to their respective means.}
\label{afoto}
\end{figure}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=.55\textwidth]{figures/figure6.pdf}}
\caption{Biases in agent-based model results relative to the district-wise errors (as a percent) in total cropland area, in terms of A) the percent of cropland in each district that was not allocated to any household, B) the land deficit, or the total area of cropland that should have been allocated to households in each district but wasn't (expressed as a percent of total district cropland, as determined by test maps), and C) the food deficit, or the percentage shortfall (relative to the reference simulation) in mean household food production resulting from inadequate cropland allocation. Dot sizes correspond to district numbers, colors represent the land cover map.}
\label{afoto}
\end{figure}

@@

\begin{figure}[!ht]
\centerline{\includegraphics[width=.55\textwidth]{figures/location_offset.pdf}}
\caption{Average nearest neighbor distances (in km) between pixels representing features identified by the reference map versus those identified from the test maps. Bar colors indicate the different features (and thus contributing maps), which were delineated by selecting pixels with values greater than the 90th percentile: densest cropland (solid bars); highest maize yield (medium transparent bars); highest carbon density (most transparent bars).}   
\label{afoto}
\end{figure}

@@

\bibliographystyle{gcbnourl} 
{\footnotesize \bibliography{/Users/lestes/Dropbox/publications/fullbib.bib}}

>>>>

\documentclass[a4paper]{article}
\usepackage[affil-it]{authblk}    
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
%\usepackage{endfloat}
\usepackage{float}
\usepackage[sort,compress]{natbib}
%\usepackage[numbers,sort,compress]{natbib}
%\bibpunct{[}{]}{,}{n}{,}{,}  % https://xianblog.wordpress.com/tag/natbib/ (allows natbib with PNAS)
\usepackage{endnotes}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage[left=2.5cm, right=2.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
%\usepackage{mathtime}
\usepackage{bm}
\usepackage{url}
%\usepackage{babel}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{boldline}
\setcellgapes{3pt}
\usepackage[flushleft]{threeparttable}
\usepackage{wrapfig}
\newcommand{\citetapos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
%%%%%

@@

%\begin{figure*}[!ht]
%%\begin{wrapfigure}{c}{1\textwidth}
%\centerline{\includegraphics[width=1\textwidth]{figures/figure1.pdf}}
%\vspace{-0.15 cm}
%\caption{(A) Errors in the percent cropland estimates resulting from each of the four test maps relative to the reference map at different scale of pixel aggregation. Rows indicate the test map being assessed (by subtraction from the reference map), while columns refer to resolution of aggregation. White indicates areas where areas under communal farmlands or permanent tree crops were removed from analysis. (B) The bias (mean error) and accuracy (mean absolute error [MAE]) of each test map at each scale of aggregation, weighted by the percentage cropland in each cell of the reference map. Bias estimates are indicated by the semi-transparent bars, accuracy (lower is more accurate) by the solid bars, with bar colors coded to specific cropland maps.}
%\label{afoto1}
%\end{figure*}

@@

%%\vspace{-0.75 cm}
%%\begin{wrapfigure}{r}{0.5\textwidth}
%\begin{figure}[!h]
%%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/biases_md_lnorm_gam_mu0.pdf}}
%\centerline{\includegraphics[width=.7\textwidth]{figures/biases_md_lnorm_gam_mu0.pdf}}
%\caption{The relationship between map accuracy (the mean absolute error) in test maps and the actual cropland cover within agricultural landscapes (reference map pixels having $>$0.5\% cropland), here defined by the boundaries of magisterial districts (n = 345), as fit with a generalized additive model. Prediction curves are color-coded to the different test maps, with the solid line indicating predicted absolute bias, and the lighter shading the standard error of the coefficients.}\label{afoto2}
%\end{figure}
%%\end{wrapfigure}
%%\vspace{-0.75 cm}

@@

%%\vspace{-0.75 cm}
%\begin{figure}[!h]
%%\begin{wrapfigure}{r}{0.5\textwidth}
%%\centerline{\includegraphics[keepaspectratio,scale = 0.4]{figures/figure3.pdf}}
%\centerline{\includegraphics[width=0.55\textwidth]{figures/figure3.pdf}}
%\caption{Biases and accuracies (mean absolute errors) of carbon densities derived from cropland maps, calculated as percents relative to the reference map. Bias estimates (represented by symbols) fall within the semi-transparent floating bars, while accuracies are contained in the solid bars. Bar colors are coded to specific cropland map, symbols indicate which cover type was used to calculate cropland-adjacent carbon density. The bar represents the mean biases calculated across each of the 5 cover types. Shrubland and grassland bias values were near zero, while secondary forest values were close to forest values, and thus these are not shown for display clarity (but see Table S2). MODIS and GlobCover values at 1 km exceeding the plot's Y limits are provided near their truncated tops.}
%\label{afoto}
%\end{figure}
%%\end{wrapfigure}

@@

SA-LC and GeoWiki also resulted in ET errors estimates along the southern and western coasts, but here the tendency was to underestimate ET, while biases in the center of the country were either negligible to absent.  All but MODIS underestimated ET by 5-15\% in the northern tip of the country.  
%
%%\vspace{-0.75 cm}
%\begin{figure}[h]
%\centerline{\includegraphics[width=.6\textwidth]{figures/et_bias_map.pdf}}
%\caption{Differences in annual mean evapotranspiration estimates from 29-year runs of the VIC land surface hydrology model when initialized with LAI response curves derived from the reference map, versus those from the four test maps.}\label{afoto}
%\end{figure}

@@

%%\vspace{-0.5 cm}
%\begin{figure}[!ht]
%%\vspace{-0.75 cm}
%\centerline{\includegraphics[width=0.55\textwidth]{figures/yield_prod_bias.pdf}}
%\caption{Bias (mean error) and accuracy (mean absolute error [MAE]) in disaggregated maize yield and production estimates. Bias estimates (represented by symbols) fall within the semi-transparent bars, mean absolute errors in the solid bars, with bar colors coded to specific cropland maps.  Symbols code the different variables (production and yield), normalized to their respective means.}
%\label{afoto}
%\end{figure}

@@

%\begin{figure}[ht]
%\centerline{\includegraphics[width=.55\textwidth]{figures/figure6.pdf}}
%\caption{Biases in agent-based model results relative to the district-wise errors (as a percent) in total cropland area, in terms of A) the percent of cropland in each district that was not allocated to any household, B) the land deficit, or the total area of cropland that should have been allocated to households in each district but wasn't (expressed as a percent of total district cropland, as determined by test maps), and C) the food deficit, or the percentage shortfall (relative to the reference simulation) in mean household food production resulting from inadequate cropland allocation. Dot sizes correspond to district numbers, colors represent the land cover map.}
%\label{afoto}
%\end{figure}

@@

%\begin{figure}[!ht]
%\centerline{\includegraphics[width=.55\textwidth]{figures/location_offset.pdf}}
%\caption{Average nearest neighbor distances (in km) between pixels representing features identified by the reference map versus those identified from the test maps. Bar colors indicate the different features (and thus contributing maps), which were delineated by selecting pixels with values greater than the 90th percentile: densest cropland (solid bars); highest maize yield (medium transparent bars); highest carbon density (most transparent bars).}   
%\label{afoto}
%\end{figure}

@@

\bibliographystyle{gcbnourl} 
%\bibliographystyle{prsb} 
{\footnotesize \bibliography{/Users/lestes/Dropbox/publications/fullbib.bib}}
